Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-10 paper/ms.tex
Add stubsection referring to lsr plot in app

>>>>

\subsection{LSR Variations} \label{ssec:lsr_var}
For similar reasons to the midplane varying across the disk, we also expect
that the local standard of rest (LSR) is a function of azimuth as well. We
perform this calculation in Appendix~\ref{app:lsr}, but in order to perform a
best-fit subtraction as in the previous section is more involved, which we
delay to future work. We do note, however, that the variation in the LSR is
less pronounced than for the midplane, at least for how we calculate the LSR.
